%-------------------------
% Resume in Latex
% Author: Jules Udahemuka
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\color{NavyBlue}
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textcolor{NavyBlue}{#2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://realjules.github.io/}{\Large\color{NavyBlue} Jules Udahemuka}} & \small{LinkedIn: \href{https://www.linkedin.com/in/jules-udahemuka/}{\textcolor{NavyBlue}{Jules Udahemuka}}}\\
  \small{Email: \href{mailto:udaheju@gmail.com}{\textcolor{NavyBlue}{udaheju@gmail.com}}} & \small{Website : \href{https://realjules.github.io/}{\textcolor{NavyBlue}{www.realjules.github.io}}}\\
  \small{Mobile: \href{tel:+250787641302}{\textcolor{NavyBlue}{(+250)78-764-102}}} & \small{Github : \href{https://github.com/realjules}{\textcolor{NavyBlue}{www.github.com/realjules}}}
\end{tabular*}

 %-----------SUMMARY-----------------
\section{Summary}
  {\small{Data-driven decision-maker specialized in AI solutions, with expertise in analytics, and ML/AI. My research in Multimodal Learning and Computer Vision includes developing algorithms that integrate visual and textual data, and applying deep learning to real-time image analysis. This work has applications in autonomous driving, medical imaging, and video surveillance. I seek a role that aligns with my passion for AI/ML and analytics.}}

%-----------EDUCATION-----------------  
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University}{Rwanda, Africa Campus}
      {Master of Science in Engineering Artificial Intelligence;  \textbf{GPA: \textcolor{NavyBlue}{3.7/4.0}}}{Aug. 2023 -- May. 2025}
    \resumeSubheading
      {University of Rwanda}{Rwanda, College of Science and Tech}
      {Bachelor of Science in Environmental Engineering; \textbf{GPA: \textcolor{NavyBlue}{3.4/4.0}}}  {Aug. 2013 -- July. 2017}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Babylon Health}{Rwanda}
      {Data Scientist}{Jun. 2022 - Jul. 2023}
      \resumeItemListStart
        \resumeItem{ML for Revenue Optimization}
          {\small{Led strategies and analyses across different departments, leveraging ML to optimize clinical operations, resulting in a \textbf{\textcolor{NavyBlue}{13.4\% revenue increase}} by minimizing unpaid consultations.}}
        \resumeItem{Decreased Fraudulent Activities}
          {\small{Decreased fraudulent consultations by \textbf{\textcolor{NavyBlue}{99.9\%}} through data-driven performance management strategies, defining metrics, and analyzing various data points.}}
      \resumeItem{Built Dashboards}
          {\small{Developed custom dashboards, enabling teams to make informed day-to-day performance decisions and drive business results.}}
      \resumeItemListEnd
      
%-------------------------------------------

    \resumeSubheading
      {Bboxx}{Rwanda}
      {BI \& Analytics Engineer}{Feb. 2020 - May. 2022}
      \resumeItemListStart
        \resumeItem{Designed and Built Data Warehouse}
          {\small{Played a key role in designing and implementing robust ETL processes using dbt, enhancing decentralized data integration from diverse sources and systems, and ensuring data accuracy.}}
        \resumeItem{Developed Dashboards}
          {\small{Created 5 Power BI dashboards with over 40 worksheets, enabling management and employees to make data-informed business decisions.}}
        \resumeItem{Won Internal Hackathon}
          {\small{Partnered on an internal hackathon machine learning project, predicting defaulters and achieving a \textbf{\textcolor{NavyBlue}{14.2\% reduction}}.}}
      \resumeItemListEnd

    \resumeSubheading
      {One Acre Fund}{Rwanda}
      {Data Analyst, Marketing}{May. 2017 - Jun. 2020}
      \resumeItemListStart
        \resumeItem{Increased Product Adoption}
          {\small{Spearheaded data-driven marketing strategies, increasing adoption rates by \textbf{\textcolor{NavyBlue}{17.7\%}} in six months through research and segmentation strategies.}}
        \resumeItem{Optimized Operations}
          {\small{Optimized retail expansion efforts, overseeing growth from 4 to 100 stores across the country in two years, supported by decentralized data gathering and live data visualization tools.}}
      \resumeItem{Increased Retention}
          {\small{Developed and implemented retention strategy, raising retention rates from \textbf{\textcolor{NavyBlue}{82\% to 93\%}} during the COVID-19 lockdown period.}}
      \resumeItemListEnd
      
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Drones Computer Vision}
      {\small{Developed an open-source project for analyzing drone footage and applying computer vision techniques like YOLO and Faster R-CNN for real-time object detection and tracking. \href{https://github.com/realjules/drone_vision}{\textcolor{blue}{{\{CODE\}}}}}} 
    \resumeSubItem{Digital Twin for Climate Change}
      {\small{Created a digital twin framework using AI and simulation to model and visualize the potential impacts of climate change on the African continent. \href{https://github.com/realjules/africa_climate_simulation}{\textcolor{blue}{{\{CODE\}}}}}}
    \resumeSubItem{Securing USSD Systems with Machine Learning}
      {\small{Implemented unsupervised anomaly detection algorithms and supervised fraud prediction models to enhance the security of USSD mobile money systems in Africa. \href{https://github.com/realjules/ussd_fraud_prediction}{\textcolor{blue}{{\{CODE\}}}} \textbar{} \href{https://arxiv.org/abs/XXXX.XXXX}{\textcolor{blue}{\{Paper\}}}}}

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
	\small{\item{
     \textbf{\textcolor{NavyBlue}{Programming Languages}}{: Python, C++, SQL} \\
     \textbf{\textcolor{NavyBlue}{ML/AI Frameworks}}{: TensorFlow, PyTorch, OpenCV, HuggingFace Transformers} \\
     \textbf{\textcolor{NavyBlue}{Data Analytics/BI}}{: dbt, Power BI, Tableau} \\
     \textbf{\textcolor{NavyBlue}{Other Skills}}{: Deep Learning, Computer Vision, NLP, MLOps, Data Warehousing, Dashboarding}
    }}
 \end{itemize}
 
%-------------------------------------------
\end{document}